From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-07-30 WOLFHPC15/article/evaluation.tex
fix 1,2,3,4 helene 30_07
fix evaluation helene 30_07

The MSL program of FullSWOF contains three mesh entities, seven computation domains, fourty-eight data and ninty-eight computations composed of thirty-two stencil computations and sixty-six local computations.

@@

%----------------------------------------
\subsection{A real case simulation}
%----------------------------------------
SkelGIS and MSD\\
Description of shallow water equations\\
MSL language description\\
The obtained series-parallel graph, comments.

%----------------------------------------
\subsection{Performances}
%----------------------------------------
\begin{itemize}
\item speedup Figures
\item number of lines (counting computation components)
\end{itemize}

>>>>

The MSL program of FullSWOF contains three mesh entities, seven computation domains, fourty-eight data and ninty-eight computations composed of thirty-two stencil kernels and sixty-six local computations.

@@

\begin{itemize}
\item speedup Figures
\item number of lines (counting computation components)
\end{itemize}
